---
title: "Demo" 
# author: "you" 
output: html_document
---

```{r, eval = TRUE, include = FALSE} 
library(stringr) 
eng_scilab <- function(options) { 
code <- str_c(options$code, collapse = "\n")  
if (options$eval) { 
flags = "--timeout 4s -ns -e" 
if(!is.null(options$timeout)) flags = paste("--timeout", options$timeout, "-ns -e") 
if(typeof(options$scilab_file) == "character") {
  exec_file <- sprintf("exec('%s', -1)", options$scilab_file) 
  code <- paste(exec_file, "\n", code)   
} 

if(!is.null(options$scilab_var)) {
  code <- paste(options$scilab_var, code) 
} 
# print(code) 
code <- paste(code, "\nexit") 
code <- paste("try;", code, ";catch;", 
              "disp('some exception was raised! :(') 
              disp('this is the exception:') 
              disp(lasterror())  
              exit; end") 
cmd <- sprintf('scilab-cli %s %s',
             flags, shQuote(code, type="sh")) 

# options$comment = NA 
out <- system(cmd, intern = TRUE) 
# print(out) 
}else{out <- ""}

knitr::engine_output(options, options$code, out)

}

knitr::knit_engines$set(scilab=eng_scilab) 
``` 

This is a simple demo for using Scilab engine in RMarkdown. Let's start, just to be sure that everythin is working, with matrix multiplication. 

```{r, engine = "scilab"} 
A = [1 2 3; 4 5 6; 7 8 9]; 
b = [1 5 25]'; 
A * b 
``` 

Sometimes, we need to multiply two really big matrices; for this, we can update the timeout. 

```{r, engine = "scilab", timeout = "15s"} 
n = 2500; 
A = rand(n, n); 
B = rand(n, n); 
tic() 
A * B; 
toc() 
``` 


Now, let's say we define a matrix in some chunk: 

```{r, engine = "scilab"} 
A = [1 2 3; 4 5 6; 7 8 9]; 
spec(A) 
``` 


And we want to reuse it in another chunk. For this, we can use `scilab_var` option. 

```{r, engine = "scilab", scilab_var = "A = [1 2 3; 4 5 6; 7 8 9];"}  
max(abs(spec(A))) // dominant eigenvalue of A 
``` 



However, one possibly needs to reuse functions and variables between chunks; writing them in one line in `scilab_var` could be really inconvenient. For this, the option `scilab_file` is available; one can load a file with whatever they want. The next chunk, for instance, compute the Fibonacci numbers with the Fibonacci function, written in [Fibonacci.sci](https://github.com/tiagodsilva/ScilabEngine/blob/main/demo/Fibonacci.sci) file. 

```{r, engine = "scilab", scilab_file = "Fibonacci.sci"}  
fibo = []; 
for i = 1:15 do fibo = [fibo Fibonacci(i)]; end 
fibo 
``` 

That is it. It is also possibly use normally all amazing functionalities of RMarkdown (for example, LaTeX with tinytex, HTML and GitHub markdown)! 







